### 2025-01-27 our_article/MCM_article/article_file.tex
论文更新

    It should be noted that the graph contains some data points that are less than zero. These values are a result of the interpolation algorithm and do not represent actual negative biomass. 
        The interpolation process sometimes generates small negative values due to the smoothing of data points, 
        especially at the boundaries of the data set or during transitions between different states of the system. 
        These negative values should be interpreted as artifacts of the numerical method and not as realistic biological quantities.
    \subsection{Selection of Parameters}
      After reviewing the literature and aligning the parameters with their real-world significance, 
      we have determined a series of parameters. Due to the large number of parameters, 
      we present the table for the main ones:
      \begin{table}[H]
        \centering
        \caption{Parameters}
        \begin{tabular}{cc}
          \toprule
          \rowcolor{customcolor!40} % 设置背景颜色
          Symbols & Description\\
          \midrule
          $123$ & 123\\
          \bottomrule
        \end{tabular}
        \label{tab:Parameters}
      \end{table}
      All of the following models will apply these parameters.

>>>>

    It should be noted that the graph contains some data points that are less than zero. 
    These values are a result of the interpolation algorithm and do not represent actual negative biomass.
